\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}

Digital twin technology has emerged as a transformative paradigm for modeling, monitoring, and optimizing complex systems across diverse domains. However, existing digital twin platforms remain domain-specific, requiring extensive manual configuration and deep technical expertise. Simultaneously, quantum computing offers computational advantages for optimization, simulation, and machine learning tasks, yet remains largely inaccessible to practitioners outside the quantum computing community. This thesis presents QTwin, a conversational quantum-powered framework for universal digital twin generation that bridges both accessibility gaps.

The QTwin platform accepts natural language system descriptions through a conversational interface powered by a spaCy-based NLP pipeline and automatically generates quantum-enhanced digital twins for any user-specified domain. The framework employs seven quantum algorithmic strategies---Quantum Approximate Optimization Algorithm (QAOA), Variational Quantum Eigensolver (VQE), Variational Quantum Classifier (VQC), quantum simulation, tree tensor networks, quantum autoencoders, and quantum sensing---implemented on the Qiskit Aer simulator. A domain-agnostic problem decomposition engine dynamically selects and composes quantum algorithms based on extracted system characteristics, eliminating the need for domain-specific code.

The framework is validated through comprehensive benchmarks across six healthcare sub-domains: personalized medicine, drug discovery, medical imaging, genomic analysis, epidemic modeling, and hospital operations. Results demonstrate consistent simulator-measured algorithmic advantage, including a 1000$\times$ throughput improvement in drug screening, $+13\%$ accuracy improvement in medical imaging classification, a 720$\times$ acceleration in epidemic simulation, and a 73\% reduction in hospital wait times. Cross-domain generalization is validated across military logistics, sports performance, and environmental disaster response scenarios without domain-specific modifications. All quantum computations were performed on the Qiskit Aer statevector simulator, which executes quantum circuits as classical matrix multiplications. The reported advantages therefore reflect \emph{algorithmic design superiority}---the quantum-inspired circuit architectures outperform traditional classical algorithms on equivalent tasks---rather than hardware-level quantum speedup. These results establish theoretical upper bounds on the advantage achievable with physical quantum processors, where noise and decoherence would reduce fidelity; hardware validation is identified as a primary direction for future work. All quantum circuits are exportable in OpenQASM format for reproducibility and future hardware deployment.

\textbf{Keywords:} Digital Twin, Quantum Computing, Conversational AI, QAOA, Natural Language Processing, Healthcare, Qiskit

\newpage
