\chapter*{Preface}
\addcontentsline{toc}{chapter}{Preface}

This thesis represents the culmination of my journey at the intersection of quantum computing, digital twin technology, and accessible artificial intelligence. When I began my graduate studies at Hamad Bin Khalifa University, I was fascinated by the transformative potential of quantum computing but troubled by its inaccessibility. The field seemed locked behind layers of mathematical formalism, specialized hardware requirements, and domain expertise that placed it beyond the reach of most practitioners.

Simultaneously, I observed that digital twin technology---despite its growing importance across industries---remained fragmented into domain-specific silos. Each application required extensive manual modeling, specialized software, and deep domain knowledge. The question that drove this research was deceptively simple: could we create a system where anyone, regardless of their technical background, could describe a system in plain language and receive a quantum-powered digital twin in return?

The QTwin platform presented in this thesis is my answer to that question. What began as a healthcare-specific prototype evolved into a universal framework capable of generating quantum digital twins for any domain. The journey from concept to working platform taught me that the most challenging problems in computer science are often not algorithmic but architectural---designing systems that are simultaneously powerful and approachable.

I hope this work contributes, in some small measure, to making quantum computing more accessible and digital twin technology more universal. The future belongs to tools that empower rather than exclude.

\vspace{1cm}
\noindent
Hassan Abdulhadi Al-Sahli\\
Doha, Qatar\\
April 2026

\newpage
