% =============================================================================
% Chapter 3: Methodology
% =============================================================================

\chapter{Methodology}
\label{ch:methodology}

This chapter presents the research methodology and technical design of the QTwin platform. Following a design science research approach grounded in the theoretical foundations of Chapter~\ref{ch:literature}, the chapter proceeds through the system architecture, conversational AI pipeline, quantum algorithm implementations, healthcare reference implementation, and benchmark methodology.

% =============================================================================
\section{Research Methodology Overview}
\label{sec:research_methodology}
% =============================================================================

This thesis adopts the design science research methodology (DSRM), which emphasizes the creation and evaluation of innovative artifacts as the central research activity. The primary artifact is the QTwin platform---an end-to-end system that accepts natural language system descriptions and produces quantum-powered digital twins. Development followed an iterative cycle of requirements analysis, architectural design, implementation, and evaluation. Functional requirements included conversational entity extraction, dynamic quantum algorithm selection, universal twin generation, and OpenQASM circuit export~\cite{cross2017openqasm, cross2022openqasm3}. Non-functional requirements encompassed sub-second NLP response latency, extensibility to new domains without code modification, and reproducibility of all quantum computations. Early prototyping revealed that spaCy's pre-trained NER was insufficient for domain-specific entities, motivating the domain-adaptive pattern matching system (Section~\ref{sec:conversational_ai_method}), and initial QAOA benchmarking prompted warm-starting strategies~\cite{farhi2014qaoa}.

The evaluation strategy combines \textit{depth validation}---quantum algorithms against classical baselines across six healthcare sub-domains with statistical significance testing---and \textit{breadth validation}---cross-domain generalization using military, sports, and environmental scenarios. The methodology addresses known concerns in quantum computing research: strong classical baselines, complete result reporting, and statistical validation with effect size analysis~\cite{preskill2018quantum}.

% =============================================================================
\section{System Architecture}
\label{sec:architecture}
% =============================================================================

% -----------------------------------------------------------------------------
\subsection{High-Level Architecture}
\label{subsec:high_level_architecture}
% -----------------------------------------------------------------------------

The QTwin platform is organized as a three-tier architecture comprising a presentation tier, an API tier, and an engine tier. This architectural pattern provides separation of concerns, enabling independent development, testing, and deployment of each tier while maintaining well-defined interfaces. The presentation tier is a Next.js~14 web application utilizing the App Router and React Server Components, providing the conversational interface through which users interact with the platform. The API tier is a FastAPI application exposing RESTful endpoints for twin management, conversation handling, benchmarking, and data retrieval, with WebSocket support for real-time conversational interaction. The engine tier encapsulates the NLP pipeline, quantum algorithm library, twin generation engine, and classical baselines. Figure~\ref{fig:system-architecture} illustrates the architecture and data flow between tiers.

\begin{figure}[htbp]
\centering
\resizebox{\textwidth}{!}{%
\begin{tikzpicture}[
  tier/.style={draw, rounded corners=4pt, minimum width=14cm, minimum height=2.8cm, font=\sffamily\bfseries, align=center},
  subbox/.style={draw, rounded corners=2pt, minimum width=2.4cm, minimum height=0.7cm, font=\sffamily\footnotesize, align=center, fill=white},
  sidedb/.style={draw, rounded corners=2pt, minimum width=2.2cm, minimum height=0.8cm, font=\sffamily\footnotesize, align=center},
  tierarrow/.style={-{Stealth[length=3mm]}, thick, qtwindark},
  dbarrow/.style={-{Stealth[length=2.5mm]}, thick, classicalgray},
  wsarrow/.style={{Stealth[length=2.5mm]}-{Stealth[length=2.5mm]}, dashed, thick, qtwinred},
]
% --- Presentation Tier ---
\node[tier, fill=qtwinblue!10, label={[font=\sffamily\bfseries]above:Presentation Tier (Next.js 14)}] (pres) at (0,6) {};
\node[subbox] (landing) at (-4.5,6) {Landing Page};
\node[subbox] (builder) at (-1.5,6) {Twin Builder};
\node[subbox] (dash) at (1.5,6) {Dashboard};
\node[subbox] (showcase) at (4.5,6) {Showcase};
% --- API Tier ---
\node[tier, fill=qtwinpurple!10, minimum width=14cm, label={[font=\sffamily\bfseries]above:API Tier (FastAPI)}] (api) at (0,3) {};
\node[subbox] (auth) at (-5,3) {Auth};
\node[subbox] (twins) at (-2.5,3) {Twins};
\node[subbox] (bench) at (0,3) {Benchmark};
\node[subbox] (data) at (2.5,3) {Data};
\node[subbox] (conv) at (5,3) {Conversation};
% --- Engine Tier ---
\node[tier, fill=qtwingreen!10, minimum width=14cm, label={[font=\sffamily\bfseries]above:Engine Tier}] (eng) at (0,0) {};
\node[subbox] (extractor) at (-4.5,0) {System Extractor};
\node[subbox] (encoder) at (-1.5,0) {Quantum Encoder};
\node[subbox] (orchestrator) at (1.8,0) {Algorithm Orchestrator};
\node[subbox] (generator) at (5,0) {Twin Generator};
% --- Side databases ---
\node[sidedb, fill=qtwinorange!15] (pg) at (9.5,3.7) {PostgreSQL 15};
\node[sidedb, fill=qtwinred!12] (redis) at (9.5,2.3) {Redis 7};
% --- Bottom quantum ---
\node[sidedb, fill=qtwinindigo!12, minimum width=3.5cm] (qiskit) at (0,-2) {Qiskit Aer + PennyLane};
% --- Arrows between tiers ---
\draw[tierarrow] (0,4.55) -- (0,4.45) node[midway, right, font=\sffamily\scriptsize] {REST/JSON};
\draw[wsarrow] (-2,4.55) -- (-2,4.45) node[midway, left, font=\sffamily\scriptsize] {WebSocket};
\draw[tierarrow] (0,1.55) -- (0,1.45);
% --- Arrows to databases ---
\draw[dbarrow] (7,3.7) -- (pg.west);
\draw[dbarrow] (7,2.3) -- (redis.west);
% --- Arrow to quantum ---
\draw[tierarrow] (0,-1.05) -- (qiskit.north);
\end{tikzpicture}%
}
\caption{Three-tier system architecture of the QTwin platform.}
\label{fig:system-architecture}
\end{figure}

Data flows sequentially through the tiers: the user submits a natural language message via WebSocket, the NLP pipeline extracts entities, and upon meeting activation thresholds the twin generation engine performs problem decomposition, algorithm selection, and quantum circuit generation---all exported in OpenQASM format~\cite{cross2017openqasm, cross2022openqasm3}. The RESTful API provides four router groups (twins, conversation, benchmark, data) with JWT authentication and PostgreSQL~15 storage with automatic SQLite fallback. Full implementation details are presented in Section~\ref{sec:platform_impl}.

% -----------------------------------------------------------------------------
\subsection{Universal Twin Generation Engine}
\label{subsec:universal_twin_engine}
% -----------------------------------------------------------------------------

The universal twin generation engine constitutes the core innovation of the QTwin platform. Unlike existing digital twin platforms that require domain-specific ontologies, pre-built simulation models, and manual configuration, the QTwin engine generates digital twins dynamically from natural language descriptions by composing domain-agnostic quantum algorithms. The engine operates as a four-stage pipeline: problem decomposition, algorithm selection, parameter encoding, and twin composition. Each stage is designed to be domain-agnostic, operating on abstract representations of entities, relationships, and objectives rather than domain-specific constructs. Figure~\ref{fig:twin_engine_pipeline} illustrates the pipeline stages.

\begin{figure}[htbp]
\centering
\resizebox{\textwidth}{!}{%
\begin{tikzpicture}[
  stagebox/.style={draw, minimum width=2.6cm, minimum height=1cm, font=\sffamily\footnotesize, align=center, thick},
  rndbox/.style={stagebox, rounded corners=6pt},
  arrw/.style={-{Stealth[length=3mm]}, thick, qtwindark},
  annot/.style={font=\sffamily\scriptsize\itshape, text=qtwindark!70, align=center},
]
% --- Pipeline boxes ---
\node[rndbox, fill=qtwingreen!20] (s1) at (0,0) {NL\\Description};
\node[stagebox, fill=qtwinblue!15] (s2) at (3.3,0) {Problem\\Decomposition};
\node[stagebox, fill=qtwinpurple!15] (s3) at (6.6,0) {Algorithm\\Selection};
\node[stagebox, fill=qtwinindigo!15] (s4) at (9.9,0) {Parameter\\Encoding};
\node[stagebox, fill=qtwincyan!15] (s5) at (13.2,0) {Twin\\Composition};
\node[rndbox, fill=qtwinorange!20] (s6) at (16.5,0) {Interactive\\Digital Twin};
% --- Arrows ---
\draw[arrw] (s1) -- (s2);
\draw[arrw] (s2) -- (s3);
\draw[arrw] (s3) -- (s4);
\draw[arrw] (s4) -- (s5);
\draw[arrw] (s5) -- (s6);
% --- Annotations ---
\node[annot, below=4pt of s1] {User text input};
\node[annot, below=4pt of s2] {Entities, relationships};
\node[annot, below=4pt of s3] {QAOA / VQE / VQC / \ldots};
\node[annot, below=4pt of s4] {Qubit mapping};
\node[annot, below=4pt of s5] {OpenQASM circuits};
\node[annot, below=4pt of s6] {Simulate, query, predict};
\end{tikzpicture}%
}
\caption{The four-stage Universal Twin Generation Engine pipeline, from natural language input to interactive digital twin output.}
\label{fig:twin_engine_pipeline}
\end{figure}

The engine achieves domain-agnosticity by separating domain-specific concerns (vocabulary, entity recognition) from domain-agnostic computation: adding a new domain requires only NLP pattern additions. The detailed operation of each pipeline stage is described in Section~\ref{sec:twin_engine}.

% -----------------------------------------------------------------------------
\subsection{Technology Stack}
\label{subsec:technology_stack}
% -----------------------------------------------------------------------------

The selection of technologies was guided by requirements of performance, extensibility, quantum computing integration, and developer productivity. Table~\ref{tab:tech_stack} presents the complete technology stack.

\begin{table}[htbp]
\centering
\caption{QTwin platform technology stack.}
\label{tab:tech_stack}
\begin{tabular}{l l l p{5.5cm}}
\hline
\textbf{Component} & \textbf{Technology} & \textbf{Version} & \textbf{Purpose} \\
\hline
Backend API & FastAPI & 0.100+ & Asynchronous REST API with OpenAPI docs, Pydantic validation \\
Frontend & Next.js & 14 & App Router, React Server Components, SSR/CSR hybrid \\
Quantum Simulator & Qiskit Aer & 0.45+ & Statevector and QASM simulation of quantum circuits \\
Differentiable QC & PennyLane & 0.33+ & Gradient-based optimization via parameter-shift rule \\
NLP Pipeline & spaCy & 3.x & Tokenization, POS tagging, NER, dependency parsing \\
Database (prod) & PostgreSQL & 15 & ACID-compliant relational storage with JSON columns \\
Database (dev) & SQLite & 3.x & Zero-configuration fallback for development \\
Cache & Redis & 7 & Circuit result caching and session management \\
3D Visualization & Three.js & r150+ & Quantum-inspired particle visualization in browser \\
Auth & python-jose & 3.3+ & JWT token generation and validation \\
Containerization & Docker Compose & 2.x & Database and cache service orchestration \\
\hline
\end{tabular}
\end{table}

FastAPI's asynchronous architecture enables concurrent quantum circuit execution. The quantum computing layer combines Qiskit Aer~\cite{aleksandrowicz2019qiskit} for simulation with PennyLane~\cite{bergholm2018pennylane} for differentiable quantum programming, while spaCy~\cite{honnibal2020spacy} provides the NLP pipeline and Redis~7 caches circuit results.

% =============================================================================
\section{Conversational AI for System Extraction}
\label{sec:conversational_ai_method}
% =============================================================================

% -----------------------------------------------------------------------------
\subsection{NLP Pipeline Design}
\label{subsec:nlp_pipeline}
% -----------------------------------------------------------------------------

The NLP pipeline transforms unstructured user input into structured system specifications suitable for digital twin generation. Built on spaCy~\cite{honnibal2020spacy}, it operates as a sequence of processing stages: tokenization, POS tagging, NER, dependency parsing, and domain-adaptive entity extraction. The first four stages leverage spaCy's pre-trained English model (\texttt{en\_core\_web\_sm}), providing robust baseline performance for general English text. The fifth stage---domain-adaptive entity extraction---is a custom component applying rule-based pattern matching to identify domain-specific entities, relationships, constraints, and goals not captured by general-purpose NER.

The pipeline defines four structured entity classes: \texttt{Entity} (with identifier, name, type, and properties dictionary representing physical or conceptual objects), \texttt{Relationship} (source and target entity identifiers, type, and strength), \texttt{Rule} (identifier, name, description, and type encoding domain logic), and \texttt{Constraint} (identifier, name, type, value, and comparison operator). Goals are extracted as simple string objectives rather than structured objects, reflecting the observation that optimization targets are typically expressed as concise directives. These classes are domain-agnostic in definition but domain-specific in instantiation, with separate pattern rule sets per domain.

Relationship inference analyzes spaCy's dependency parse tree: when two entities are connected through a dependency path of length three or fewer, a relationship is inferred with type determined by the intervening verb or preposition. Confidence scoring considers pattern specificity and entity frequency; low-confidence items are flagged for clarification. The extraction procedure is presented in Listing~\ref{lst:entity_extraction}.

\begin{lstlisting}[caption={Domain-agnostic entity extraction algorithm.}, label={lst:entity_extraction}]
PROCEDURE ExtractEntities(D, V)
  INPUT: Natural language description D
         Domain vocabulary V = {V_healthcare, V_manufacturing, ...}
  OUTPUT: Entities E, Relationships R, Constraints C, Goals G

  doc <- SpaCyParse(D)           // Tokenize, POS tag, NER, parse
  E <- {}, R <- {}, C <- {}, G <- {}
  domain <- ClassifyDomain(doc, V)  // Identify most likely domain
  patterns <- V[domain]             // Load domain-specific patterns

  FOR each token span s IN doc DO
    IF MatchPattern(s, patterns.entities) THEN
      e <- CreateEntity(s, EntityType(s))
      e.confidence <- ComputeConfidence(s, patterns)
      E <- E UNION {e}
    ELSE IF MatchPattern(s, patterns.constraints) THEN
      C <- C UNION {CreateConstraint(s)}
    ELSE IF MatchPattern(s, patterns.goals) THEN
      G <- G UNION {CreateGoal(s)}
    END IF
  END FOR

  FOR each pair (e_i, e_j) IN E x E within same sentence DO
    path <- DependencyPath(e_i, e_j, doc)
    IF |path| <= 3 THEN
      rel_type <- InferRelationType(path)
      R <- R UNION {(e_i, rel_type, e_j)}
    END IF
  END FOR

  RETURN E, R, C, G
END PROCEDURE
\end{lstlisting}

% -----------------------------------------------------------------------------
\subsection{Problem Type Classification}
\label{subsec:problem_classification}
% -----------------------------------------------------------------------------

Problem type classification determines the computational nature of the user's system description, which in turn drives the selection of quantum algorithms. The platform recognizes six problem types forming a taxonomy that covers the principal computational task categories in digital twin applications: \textit{optimization} (finding the best configuration among discrete alternatives), \textit{classification} (assigning entities to categories based on features), \textit{simulation} (modeling temporal evolution), \textit{anomaly detection} (identifying deviations from expected behavior), \textit{correlation analysis} (discovering relationships among variables), and \textit{sensing} (integrating sensor measurements). Each maps to one or more quantum algorithms as specified in Table~\ref{tab:algorithm_mapping}.

\begin{table}[htbp]
\centering
\caption{Mapping of problem types to quantum algorithms and representative application examples.}
\label{tab:algorithm_mapping}
\begin{tabular}{l l p{6cm}}
\hline
\textbf{Problem Type} & \textbf{Algorithm} & \textbf{Example Application} \\
\hline
Combinatorial Optimization & QAOA & Route planning, scheduling, resource allocation \\
Classification & VQC & Patient classification, fraud detection, quality assessment \\
Anomaly Detection & Quantum Autoencoder & Sensor anomaly detection, outlier identification \\
Correlation Analysis & Tree Tensor Network & Gene interaction discovery, feature correlation \\
Sensor Integration & Quantum Sensing DT & Environmental monitoring, precision measurement \\
Complex Modeling & Neural Quantum DT & Hybrid quantum-classical predictions, system modeling \\
Population Dynamics & Quantum Simulation & Epidemic modeling, agent-based dynamics \\
\hline
\end{tabular}
\end{table}

Classification uses a rule-based decision tree: optimization keywords $\rightarrow$ \textit{optimization}, categorization goals $\rightarrow$ \textit{classification}, dynamic processes $\rightarrow$ \textit{simulation}, fault detection $\rightarrow$ \textit{anomaly detection}, high-dimensional correlations $\rightarrow$ \textit{correlation analysis}, physical sensors $\rightarrow$ \textit{sensing}. Compound types trigger multiple algorithm selections~\cite{cerezo2021variational}.

% -----------------------------------------------------------------------------
\subsection{Conversation State Machine}
\label{subsec:conversation_state_machine}
% -----------------------------------------------------------------------------

The conversational interface is governed by a finite state machine defining six states: \texttt{GREETING}, \texttt{PROBLEM\_DESCRIPTION}, \texttt{CLARIFYING\_QUESTIONS}, \texttt{DATA\_REQUEST}, \texttt{CONFIRMATION}, and \texttt{GENERATION}. Each state corresponds to a phase of information gathering, and transitions are triggered by the completeness of the extracted specification. Figure~\ref{fig:state_machine} illustrates the state machine and its transition conditions.

The \texttt{GREETING} state handles initial interaction; \texttt{PROBLEM\_DESCRIPTION} captures the user's system description and classifies the application domain via keyword confidence scoring across ten supported domains (healthcare, sports, military, environment, finance, logistics, manufacturing, social, science, and general); \texttt{CLARIFYING\_QUESTIONS} actively solicits additional system details when entities or goals are incomplete; \texttt{DATA\_REQUEST} prompts for quantitative parameters, constraints, and data sources; and \texttt{CONFIRMATION} presents a summary of the extracted specification for user validation. The transition to \texttt{GENERATION} requires at least two entities, one relationship, and one goal. Upon successful generation, the twin's status transitions from \texttt{DRAFT} to \texttt{ACTIVE}---a lifecycle transition managed by the separate \texttt{TwinStatus} enumeration rather than the conversation state machine, persisted in the database and reflected in the frontend.

The state machine supports backward transitions: additional entity information arriving during goal clarification is processed without formal state transitions, and edge cases such as single-message descriptions or contradictory inputs are handled through rapid transitions and clarification requests respectively.

\begin{figure}[htbp]
\centering
\resizebox{\textwidth}{!}{%
\begin{tikzpicture}[
  state/.style={draw, rounded corners=4pt, minimum width=2.8cm, minimum height=0.9cm, font=\sffamily\footnotesize\bfseries, align=center, thick},
  terminal/.style={draw, double, rounded corners=4pt, minimum width=2.8cm, minimum height=0.9cm, font=\sffamily\footnotesize\bfseries, align=center, thick, fill=qtwingreen!20},
  fwd/.style={-{Stealth[length=2.5mm]}, thick, qtwindark},
  back/.style={-{Stealth[length=2.5mm]}, dashed, thick, qtwinred!70},
  elabel/.style={font=\sffamily\tiny, fill=white, inner sep=1pt},
]
% --- States: zigzag layout ---
\node[state, fill=qtwinblue!15] (greet) at (0,0) {GREETING};
\node[state, fill=qtwinblue!20] (prob) at (4,0) {PROBLEM\\DESCRIPTION};
\node[state, fill=qtwinpurple!15] (clar) at (8,0) {CLARIFYING\\QUESTIONS};
\node[state, fill=qtwinpurple!20] (datareq) at (12,0) {DATA\\REQUEST};
\node[state, fill=qtwinpurple!22] (conf) at (16,0) {CONFIRMATION};
\node[state, fill=qtwinpurple!25] (gen) at (20,0) {GENERATION};
\node[terminal] (active) at (24,0) {ACTIVE\\TWIN};
% --- Forward arrows ---
\draw[fwd] (greet) -- (prob) node[elabel, midway, above] {domain detected};
\draw[fwd] (prob) -- (clar) node[elabel, midway, above] {entities found};
\draw[fwd] (clar) -- (datareq) node[elabel, midway, above] {goals identified};
\draw[fwd] (datareq) -- (conf) node[elabel, midway, above] {data discussed};
\draw[fwd] (conf) -- (gen) node[elabel, midway, above] {user confirms};
\draw[fwd] (gen) -- (active) node[elabel, midway, above] {threshold met};
% --- Backward arrows ---
\draw[back] (clar.south) .. controls (6,-1.3) and (5.5,-1.3) .. (prob.south) node[elabel, midway, below] {new entities};
\draw[back] (conf.south) .. controls (13,-1.3) and (10,-1.3) .. (clar.south east) node[elabel, midway, below] {refine};
\end{tikzpicture}%
}
\caption{Conversation state machine governing information gathering from initial greeting through twin generation. The twin lifecycle status (DRAFT to ACTIVE) is managed by a separate enumeration.}
\label{fig:state_machine}
\end{figure}

% -----------------------------------------------------------------------------
\subsection{Provider Abstraction}
\label{subsec:provider_abstraction}
% -----------------------------------------------------------------------------

A provider abstraction layer separates the twin generation engine from the NLP implementation. Two concrete providers are implemented: the \texttt{LocalProvider} using the rule-based spaCy pipeline for deterministic behavior, and the \texttt{AnthropicProvider} using Anthropic's Claude API for enhanced extraction. A provider abstraction layer with a common base class enables swapping between providers without modifying downstream code.

% =============================================================================
\section{Universal Twin Generation Engine}
\label{sec:twin_engine}
% =============================================================================

This section details each stage of the universal twin generation engine's four-stage pipeline: problem decomposition, algorithm selection, parameter encoding, and twin composition.

% -----------------------------------------------------------------------------
\subsection{Problem Decomposition}
\label{subsec:problem_decomposition}
% -----------------------------------------------------------------------------

The problem decomposition algorithm transforms the output of entity extraction---a collection of entities, relationships, constraints, and goals---into a structured problem specification comprising four components: the \textit{problem type} (one of the six categories defined in Section~\ref{subsec:problem_classification}), the \textit{variables} (entities and properties constituting the problem's degrees of freedom), the \textit{objective function} (expression of the goal to be optimized), and the \textit{constraints} (conditions that valid solutions must satisfy). Listing~\ref{lst:problem_decomposition} presents the decomposition procedure.

\begin{lstlisting}[caption={Problem decomposition algorithm.}, label={lst:problem_decomposition}]
PROCEDURE DecomposeProblem(E, R, C, G)
  INPUT: Entities E, Relationships R, Constraints C, Goals G
  OUTPUT: Problem specification P = (type, vars, objective, constraints)

  type <- ClassifyProblem(E, G)   // Apply decision tree
  vars <- {}

  FOR each entity e IN E DO
    IF e.type = SYSTEM_ENTITY AND e.confidence >= tau THEN
      vars <- vars UNION {(e.name, e.properties)}
    END IF
  END FOR

  objective <- FormulateObjective(type, G, R)
  constraints_formal <- FormalizeConstraints(C, vars)
  P <- (type, vars, objective, constraints_formal)

  RETURN P
END PROCEDURE
\end{lstlisting}

The algorithm classifies the problem type, extracts variables from entities exceeding confidence threshold $\tau = 0.1$, and formalizes constraints as mathematical expressions. Compound problems produce multiple specifications that the twin composition stage integrates.

% -----------------------------------------------------------------------------
\subsection{Algorithm Selection}
\label{subsec:algorithm_selection}
% -----------------------------------------------------------------------------

Algorithm selection maps each problem specification onto quantum algorithms from the platform's library. The selection follows a decision tree that uses problem type as the primary discriminant and problem characteristics (variable count, data type, qubit budget) as secondary factors. For optimization, QAOA~\cite{farhi2014qaoa} is selected with depth $p$ scaled by problem size ($p = 1$ for $<$8 variables, $p = 2$ for 8--15, $p = 3$ for larger). For classification, VQC~\cite{schuld2020circuit} is selected with architecture variations adapted to dataset size: deeper variational circuits with additional entangling layers for larger datasets ($>$50 samples) where variational training can exploit the data volume, and shallower circuits with fewer parameters for smaller datasets to mitigate overfitting. For anomaly detection, the quantum autoencoder~\cite{romero2017quantum} is selected; for correlation analysis, the tree tensor network~\cite{orus2019tensor, huggins2019towards}; for sensing, the quantum sensing module~\cite{degen2017quantum}; and for complex modeling, the neural quantum digital twin~\cite{cong2019quantum}. Figure~\ref{fig:algorithm-mapping} illustrates this taxonomy.

\begin{figure}[htbp]
\centering
\resizebox{\textwidth}{!}{%
\begin{tikzpicture}[
  lbox/.style={draw, rounded corners=4pt, minimum width=3.8cm, minimum height=0.7cm, font=\sffamily\footnotesize, align=center, fill=qtwinblue!15, thick},
  rbox/.style={draw, rounded corners=4pt, minimum width=3.2cm, minimum height=0.7cm, font=\sffamily\footnotesize, align=center, fill=qtwinpurple!15, thick},
  primary/.style={-{Stealth[length=2.5mm]}, thick, qtwindark},
  secondary/.style={-{Stealth[length=2.5mm]}, dashed, thick, classicalgray},
  fwlabel/.style={font=\sffamily\tiny\itshape, text=qtwindark!60},
]
% --- Left column (problem types) ---
\node[lbox] (opt) at (0, 0)   {Combinatorial Optimization};
\node[lbox] (cls) at (0,-1.2) {Classification};
\node[lbox] (mol) at (0,-2.4) {Molecular Simulation};
\node[lbox] (cor) at (0,-3.6) {Correlation Analysis};
\node[lbox] (ano) at (0,-4.8) {Anomaly Detection};
\node[lbox] (cmp) at (0,-6.0) {Complex Modeling};
\node[lbox] (pop) at (0,-7.2) {Population Dynamics};
% --- Right column (algorithms) ---
\node[rbox] (qaoa) at (8, 0)   {QAOA};
\node[rbox] (vqc)  at (8,-1.2) {VQC};
\node[rbox] (vqe)  at (8,-2.4) {VQE};
\node[rbox] (ttn)  at (8,-3.6) {Tree Tensor Network};
\node[rbox] (qae)  at (8,-4.8) {Quantum Autoencoder};
\node[rbox] (nqdt) at (8,-6.0) {Neural Quantum DT};
\node[rbox] (qsim) at (8,-7.2) {Quantum Simulation};
% --- Framework labels ---
\node[fwlabel, below=1pt of qaoa] {(Qiskit)};
\node[fwlabel, below=1pt of vqc]  {(PennyLane)};
\node[fwlabel, below=1pt of vqe]  {(Qiskit)};
\node[fwlabel, below=1pt of ttn]  {(PennyLane)};
\node[fwlabel, below=1pt of qae]  {(PennyLane)};
\node[fwlabel, below=1pt of nqdt] {(PennyLane)};
\node[fwlabel, below=1pt of qsim] {(Qiskit)};
% --- Primary mappings ---
\draw[primary] (opt.east) -- (qaoa.west);
\draw[primary] (cls.east) -- (vqc.west);
\draw[primary] (mol.east) -- (vqe.west);
\draw[primary] (cor.east) -- (ttn.west);
\draw[primary] (ano.east) -- (qae.west);
\draw[primary] (cmp.east) -- (nqdt.west);
\draw[primary] (pop.east) -- (qsim.west);
% --- Secondary mappings ---
\draw[secondary] (opt.east) -- (vqe.west);
\draw[secondary] (cls.east) -- (nqdt.west);
\end{tikzpicture}%
}
\caption{Problem type taxonomy and quantum algorithm mapping.}
\label{fig:algorithm-mapping}
\end{figure}

A fallback mechanism automatically executes the classical baseline if quantum execution fails (Section~\ref{subsec:classical_fallback}). For complex twins, the selection logic composes algorithms in pipeline or parallel based on data dependencies.


% -----------------------------------------------------------------------------
\subsection{Quantum Encoding Strategies}
\label{subsec:quantum_encoding}
% -----------------------------------------------------------------------------

The platform implements three encoding strategies for mapping classical data to quantum states~\cite{nielsen2010quantum}.

\textit{Amplitude encoding} maps a normalized data vector $\mathbf{x} = (x_0, \ldots, x_{N-1})$ into the amplitudes of a quantum state:
\begin{equation}
|\psi\rangle = \sum_{i=0}^{N-1} x_i |i\rangle, \quad \text{where } \sum_{i=0}^{N-1} |x_i|^2 = 1.
\label{eq:amplitude_encoding}
\end{equation}
This requires only $n = \lceil \log_2 N \rceil$ qubits for $N$ values but $O(N)$ preparation gates~\cite{nielsen2010quantum}. It is used by the quantum autoencoder.

\textit{Angle encoding} maps each data value $x_i$ to a rotation angle on a dedicated qubit:
\begin{equation}
|\psi\rangle = \bigotimes_{i=1}^{n} R_y\!\left(2\arcsin\!\left(\sqrt{x_i}\right)\right)|0\rangle,
\label{eq:angle_encoding}
\end{equation}
where $R_y(\theta) = e^{-i\theta Y/2}$. This NISQ-friendly encoding requires $n$ qubits for $n$ features with only $n$ single-qubit gates~\cite{schuld2020circuit}, and is the default for VQC and the neural quantum digital twin~\cite{cerezo2021variational}.

\textit{Basis encoding} maps categorical or binary data into computational basis states:
\begin{equation}
|\psi\rangle = |b_1 b_2 \cdots b_n\rangle.
\label{eq:basis_encoding}
\end{equation}
This is used by QAOA, where binary variables are naturally represented in the computational basis~\cite{farhi2014qaoa}. A \textit{hybrid encoding} strategy combines approaches for mixed data types, with automatic selection based on algorithm requirements.

% -----------------------------------------------------------------------------
\subsection{Dynamic Twin Composition}
\label{subsec:twin_composition}
% -----------------------------------------------------------------------------

The twin composition stage assembles the outputs of one or more quantum algorithm executions into a coherent digital twin comprising \texttt{entities}, \texttt{relationships}, \texttt{quantum\_circuits} (OpenQASM), \texttt{metrics}, and \texttt{visualization} parameters. For multi-algorithm twins, a merging protocol maps each algorithm's results to the appropriate twin components. The standardized \texttt{QuantumResult} structure provides a uniform interface for composition, and real-time WebSocket updates enable incremental twin refinement.

% -----------------------------------------------------------------------------
\subsection{Classical Fallback}
\label{subsec:classical_fallback}
% -----------------------------------------------------------------------------

Every quantum algorithm is paired with a classical counterpart (e.g., genetic algorithms~\cite{holland1975adaptation} for QAOA, random forest/SVM~\cite{cortes1995support} for VQC, PCA for the autoencoder). Fallback is triggered by quantum execution failure, qubit limit exceeded, or explicit user preference. All fallbacks set \texttt{used\_quantum = False} with documented reasons, ensuring benchmarking results are not contaminated by silent fallbacks.

% -----------------------------------------------------------------------------
\subsection{OpenQASM Export}
\label{subsec:openqasm_export}
% -----------------------------------------------------------------------------

All quantum circuits are exported in OpenQASM~2.0 format~\cite{cross2017openqasm} via Qiskit's \texttt{qasm()} method, with OpenQASM~3.0 support for advanced constructs~\cite{cross2022openqasm3}. Exports include metadata annotations (problem type, algorithm, optimized parameters, timestamp) embedded as comments, and are compatible with any OpenQASM-compliant backend, facilitating transition from simulation to hardware execution~\cite{aleksandrowicz2019qiskit}.

% =============================================================================
\section{Quantum Algorithm Implementations}
\label{sec:quantum_algo_impl}
% =============================================================================

% -----------------------------------------------------------------------------
\subsection{QAOA for Combinatorial Optimization}
\label{subsec:qaoa_implementation}
% -----------------------------------------------------------------------------

The Quantum Approximate Optimization Algorithm (QAOA)~\cite{farhi2014qaoa} is the platform's primary algorithm for combinatorial optimization. QAOA approximates the ground state of a problem Hamiltonian $H_P$ through the alternating application of problem and mixer unitaries over $p$ layers, beginning from the uniform superposition $|+\rangle^{\otimes n}$. The resulting parameterized state is:
\begin{equation}
|\boldsymbol{\gamma}, \boldsymbol{\beta}\rangle = U_M(\beta_p)\, U_P(\gamma_p) \cdots U_M(\beta_1)\, U_P(\gamma_1) |+\rangle^{\otimes n},
\label{eq:qaoa_state_impl}
\end{equation}
where $U_P(\gamma) = e^{-i\gamma H_P}$ is the problem unitary and $U_M(\beta) = e^{-i\beta H_M}$ is the mixer unitary with $H_M = \sum_j X_j$. The cost function minimized is the expectation value of the problem Hamiltonian:
\begin{equation}
C(\boldsymbol{\gamma}, \boldsymbol{\beta}) = \langle \boldsymbol{\gamma}, \boldsymbol{\beta} | H_C | \boldsymbol{\gamma}, \boldsymbol{\beta} \rangle,
\label{eq:qaoa_cost}
\end{equation}
estimated from measurement outcomes and minimized using a classical optimizer. Figure~\ref{fig:qaoa-circuit} illustrates the circuit structure.

\begin{figure}[htbp]
\centering
\resizebox{\textwidth}{!}{%
\begin{tikzpicture}[
  gate/.style={draw, fill=white, minimum width=0.6cm, minimum height=0.6cm, font=\footnotesize, align=center, thick},
  biggate/.style={draw, rounded corners=2pt, minimum width=1.2cm, font=\footnotesize, align=center, thick},
  meter/.style={draw, fill=white, minimum width=0.6cm, minimum height=0.6cm, font=\footnotesize, thick},
  wire/.style={thick},
  brace/.style={decorate, decoration={brace, amplitude=5pt, raise=3pt}, thick},
]
% --- Qubit wires ---
\foreach \i in {0,...,3} {
  \draw[wire] (-0.5, -\i*1.0) -- (14.5, -\i*1.0);
  \node[font=\footnotesize, anchor=east] at (-0.7, -\i*1.0) {$|0\rangle$};
}
% --- Hadamard gates ---
\foreach \i in {0,...,3} {
  \node[gate] at (0.5, -\i*1.0) {$H$};
}
% --- QAOA Layer 1 ---
\node[biggate, fill=qtwinblue!20, minimum height=3.6cm] (up1) at (2.8, -1.5) {$U_P(\gamma_1)$};
\node[biggate, fill=qtwinpurple!20, minimum height=3.6cm] (um1) at (4.6, -1.5) {$U_M(\beta_1)$};
% --- QAOA Layer 2 ---
\node[biggate, fill=qtwinblue!20, minimum height=3.6cm] (up2) at (7.0, -1.5) {$U_P(\gamma_2)$};
\node[biggate, fill=qtwinpurple!20, minimum height=3.6cm] (um2) at (8.8, -1.5) {$U_M(\beta_2)$};
% --- Braces for layers ---
\draw[brace] (2.1, 0.55) -- (5.3, 0.55) node[midway, above=8pt, font=\footnotesize] {Layer 1 ($p{=}1$)};
\draw[brace] (6.3, 0.55) -- (9.5, 0.55) node[midway, above=8pt, font=\footnotesize] {Layer 2 ($p{=}2$)};
% --- Measurement ---
\foreach \i in {0,...,3} {
  \node[meter] (m\i) at (11.5, -\i*1.0) {$M$};
  % meter decoration: small arc
  \draw[thick] (11.25, -\i*1.0+0.15) arc[start angle=180, end angle=0, radius=0.25];
  \draw[thick, -{Stealth[length=1.5mm]}] (11.5, -\i*1.0+0.15) -- (11.65, -\i*1.0+0.35);
}
% --- Classical output lines ---
\foreach \i in {0,...,3} {
  \draw[thick, double] (11.8, -\i*1.0) -- (12.5, -\i*1.0);
}
\end{tikzpicture}%
}
\caption{QAOA circuit structure for $p=2$ layers.}
\label{fig:qaoa-circuit}
\end{figure}

For resource allocation and scheduling, the optimization is formulated as QUBO, mapped to an Ising Hamiltonian via $z_i = (1 - \sigma_i^z)/2$ with constraints incorporated through penalty terms~\cite{nielsen2010quantum}. Parameters are optimized via the derivative-free COBYLA optimizer~\cite{cerezo2021variational}, with $p = 1$ for problems up to 8 variables and $p = 2$ for larger instances~\cite{farhi2014qaoa}. Warm-starting reuses parameters from structurally similar problems. The full circuit procedure is provided in Appendix~A.

% -----------------------------------------------------------------------------
\subsection{Variational Quantum Classifier}
\label{subsec:vqc_implementation}
% -----------------------------------------------------------------------------

The Variational Quantum Classifier (VQC)~\cite{schuld2020circuit, cerezo2021variational} is the platform's primary algorithm for classification tasks. The VQC architecture comprises three stages: a data encoding layer using angle encoding (Equation~\ref{eq:angle_encoding}) to map features to qubit rotations, a variational layer of $L$ strongly entangling layers each comprising $R_y(\theta_{l,i})R_z(\phi_{l,i})$ rotations on every qubit followed by CNOT entanglement, and a measurement layer mapping the Pauli-$Z$ expectation value to class probabilities via the sigmoid function. Multi-class classification uses a one-versus-rest strategy. Figure~\ref{fig:vqc-circuit} illustrates the circuit architecture.

\begin{figure}[htbp]
\centering
\resizebox{\textwidth}{!}{%
\begin{tikzpicture}[
  gate/.style={draw, fill=white, minimum width=0.7cm, minimum height=0.55cm, font=\scriptsize, align=center, thick},
  ggreen/.style={gate, fill=qtwingreen!20},
  gpurple/.style={gate, fill=qtwinpurple!20},
  meter/.style={draw, fill=white, minimum width=0.6cm, minimum height=0.6cm, font=\footnotesize, thick},
  wire/.style={thick},
  brace/.style={decorate, decoration={brace, amplitude=5pt, raise=3pt}, thick},
  cnottgt/.style={draw, circle, inner sep=0pt, minimum size=6pt, thick, fill=white},
  cnotctrl/.style={fill=qtwindark, circle, inner sep=0pt, minimum size=3pt},
]
% --- Qubit wires ---
\foreach \i in {0,...,3} {
  \draw[wire] (-0.5, -\i*1.1) -- (20, -\i*1.1);
  \node[font=\footnotesize, anchor=east] at (-0.7, -\i*1.1) {$|0\rangle$};
}
% --- Feature Map (encoding) ---
\node[ggreen] at (0.8, 0)    {$R_Y(x_1)$};
\node[ggreen] at (0.8, -1.1) {$R_Y(x_2)$};
\node[ggreen] at (0.8, -2.2) {$R_Y(x_3)$};
\node[ggreen] at (0.8, -3.3) {$R_Y(x_4)$};
% --- Ansatz Layer 1: rotations ---
\node[gpurple] at (3.0, 0)    {$R_Y$};
\node[gpurple] at (3.8, 0)    {$R_Z$};
\node[gpurple] at (3.0, -1.1) {$R_Y$};
\node[gpurple] at (3.8, -1.1) {$R_Z$};
\node[gpurple] at (3.0, -2.2) {$R_Y$};
\node[gpurple] at (3.8, -2.2) {$R_Z$};
\node[gpurple] at (3.0, -3.3) {$R_Y$};
\node[gpurple] at (3.8, -3.3) {$R_Z$};
% --- Ansatz Layer 1: CNOTs ---
% CNOT 0->1
\node[cnotctrl] at (5.0, 0) {};
\draw[thick] (5.0, 0) -- (5.0, -1.1);
\node[cnottgt] at (5.0, -1.1) {};
\draw[thick] (4.94, -1.1) -- (5.06, -1.1);
\draw[thick] (5.0, -1.16) -- (5.0, -1.04);
% CNOT 1->2
\node[cnotctrl] at (5.6, -1.1) {};
\draw[thick] (5.6, -1.1) -- (5.6, -2.2);
\node[cnottgt] at (5.6, -2.2) {};
\draw[thick] (5.54, -2.2) -- (5.66, -2.2);
\draw[thick] (5.6, -2.26) -- (5.6, -2.14);
% CNOT 2->3
\node[cnotctrl] at (6.2, -2.2) {};
\draw[thick] (6.2, -2.2) -- (6.2, -3.3);
\node[cnottgt] at (6.2, -3.3) {};
\draw[thick] (6.14, -3.3) -- (6.26, -3.3);
\draw[thick] (6.2, -3.36) -- (6.2, -3.24);
% --- Ansatz Layer 2: rotations ---
\node[gpurple] at (8.0, 0)    {$R_Y$};
\node[gpurple] at (8.8, 0)    {$R_Z$};
\node[gpurple] at (8.0, -1.1) {$R_Y$};
\node[gpurple] at (8.8, -1.1) {$R_Z$};
\node[gpurple] at (8.0, -2.2) {$R_Y$};
\node[gpurple] at (8.8, -2.2) {$R_Z$};
\node[gpurple] at (8.0, -3.3) {$R_Y$};
\node[gpurple] at (8.8, -3.3) {$R_Z$};
% --- Ansatz Layer 2: CNOTs ---
% CNOT 0->1
\node[cnotctrl] at (10.0, 0) {};
\draw[thick] (10.0, 0) -- (10.0, -1.1);
\node[cnottgt] at (10.0, -1.1) {};
\draw[thick] (9.94, -1.1) -- (10.06, -1.1);
\draw[thick] (10.0, -1.16) -- (10.0, -1.04);
% CNOT 1->2
\node[cnotctrl] at (10.6, -1.1) {};
\draw[thick] (10.6, -1.1) -- (10.6, -2.2);
\node[cnottgt] at (10.6, -2.2) {};
\draw[thick] (10.54, -2.2) -- (10.66, -2.2);
\draw[thick] (10.6, -2.26) -- (10.6, -2.14);
% CNOT 2->3
\node[cnotctrl] at (11.2, -2.2) {};
\draw[thick] (11.2, -2.2) -- (11.2, -3.3);
\node[cnottgt] at (11.2, -3.3) {};
\draw[thick] (11.14, -3.3) -- (11.26, -3.3);
\draw[thick] (11.2, -3.36) -- (11.2, -3.24);
% --- Braces ---
\draw[brace] (0.3, 0.55) -- (1.3, 0.55) node[midway, above=8pt, font=\footnotesize] {Feature Map};
\draw[brace] (2.5, 0.55) -- (6.7, 0.55) node[midway, above=8pt, font=\footnotesize] {Ansatz Layer 1};
\draw[brace] (7.5, 0.55) -- (11.7, 0.55) node[midway, above=8pt, font=\footnotesize] {Ansatz Layer 2};
% --- Measurement ---
\foreach \i in {0,...,3} {
  \node[meter] (m\i) at (13.0, -\i*1.1) {$M$};
  \draw[thick] (12.75, -\i*1.1+0.15) arc[start angle=180, end angle=0, radius=0.25];
  \draw[thick, -{Stealth[length=1.5mm]}] (13.0, -\i*1.1+0.15) -- (13.15, -\i*1.1+0.35);
}
\foreach \i in {0,...,3} {
  \draw[thick, double] (13.3, -\i*1.1) -- (14.0, -\i*1.1);
}
\end{tikzpicture}%
}
\caption{VQC circuit structure with angle encoding and variational ansatz.}
\label{fig:vqc-circuit}
\end{figure}

Training uses the parameter-shift rule~\cite{mcclean2016theory} for exact gradient computation, driving an Adam optimizer~\cite{kingma2015adam} with cross-entropy loss via PennyLane~\cite{bergholm2018pennylane}. The number of variational layers $L$ scales with qubit count, and restricted initialization ($[-\pi/4, \pi/4]$) mitigates barren plateaus~\cite{mcclean2018barren}.

% -----------------------------------------------------------------------------
\subsection{Quantum Sensing Digital Twin}
\label{subsec:quantum_sensing}
% -----------------------------------------------------------------------------

The quantum sensing module implements quantum-enhanced parameter estimation~\cite{degen2017quantum}, exploiting entanglement to surpass the classical standard quantum limit ($\Delta\theta \geq 1/\sqrt{N}$) and approach the Heisenberg limit ($\Delta\theta \geq 1/N$)---a quadratic precision improvement. The implementation prepares GHZ states via Hadamard and CNOT cascades, accumulates phase through $R_Z$ rotations proportional to sensor readings, and processes measurements through maximum likelihood estimation with uncertainty bounds. Iterative refinement produces progressively more precise estimates, mirroring continuous digital twin data integration.

% -----------------------------------------------------------------------------
\subsection{Neural Quantum Digital Twin}
\label{subsec:neural_quantum}
% -----------------------------------------------------------------------------

The Neural Quantum Digital Twin implements a hybrid quantum-classical neural network~\cite{cong2019quantum, cerezo2021variational} following a sandwich architecture: classical input layers perform dimensionality reduction, quantum encoding maps the compact representation to qubit rotations via angle encoding (Equation~\ref{eq:angle_encoding}), quantum variational layers apply $L$ layers of $R_Y$ and $R_Z$ rotations with CNOT entanglement, measurement extracts expectation values, and classical output layers perform final prediction. Training uses backpropagation for classical layers and the parameter-shift rule~\cite{mcclean2016theory} for quantum layers, with PennyLane~\cite{bergholm2018pennylane} providing end-to-end integration.

% -----------------------------------------------------------------------------
\subsection{Tree Tensor Network}
\label{subsec:tree_tensor_network}
% -----------------------------------------------------------------------------

The Tree Tensor Network (TTN) implements hierarchical tensor decomposition for discovering correlation structures in high-dimensional data~\cite{orus2019tensor, huggins2019towards}. Input variables are organized in a binary tree where leaves correspond to individual features and internal nodes perform tensor contractions, progressively combining pairs into higher-level representations. The hierarchical structure captures correlations at multiple scales:
\begin{equation}
|\Psi\rangle = \sum_{i_1, i_2, \ldots, i_n} T^{(1)}_{i_1 i_2} T^{(2)}_{i_3 i_4} \cdots T^{(\text{root})} |i_1 i_2 \cdots i_n\rangle,
\label{eq:ttn_state}
\end{equation}
where the tensor contractions proceed hierarchically from leaves to root~\cite{orus2019tensor}. The quantum implementation maps each tensor contraction to a two-qubit subcircuit (Hadamard gates, parameterized $R_Y$ rotations, CNOT gates), with alternating even-odd and odd-even qubit pairings across layers~\cite{huggins2019towards}. Parameters are trained jointly to minimize task-specific loss functions.

% -----------------------------------------------------------------------------
\subsection{Quantum Autoencoder}
\label{subsec:quantum_autoencoder}
% -----------------------------------------------------------------------------

The quantum autoencoder implements anomaly detection through learned compression of normal data distributions~\cite{romero2017quantum}. Operating on $n$ qubits with $k < n$ latent qubits, the encoder $U_E(\boldsymbol{\theta})$ compresses input data so that trash qubits return to $|0\rangle$ when compression succeeds. Training minimizes reconstruction error---estimated by measuring the probability that trash qubits are in $|0\rangle$---via the parameter-shift rule~\cite{mcclean2016theory}. At inference, the anomaly score $1 - P(|0\rangle^{\otimes (n-k)})$ identifies data points that resist compression, suitable for digital twin scenarios where the space of possible anomalies is vast~\cite{cerezo2021variational}.

% =============================================================================
\section{Healthcare Reference Implementation}
\label{sec:healthcare_impl}
% =============================================================================

Healthcare serves as the primary validation domain, selected because it encompasses diverse computational task types (optimization, classification, simulation, anomaly detection, correlation analysis), public datasets and established classical baselines exist for meaningful comparison, and improvements carry significant societal value~\cite{tao2018digital}. Six modules each exercise a different quantum algorithm and validate a different aspect of the universal engine.

% -----------------------------------------------------------------------------
\subsection{Personalized Medicine Module}
\label{subsec:personalized_medicine_method}
% -----------------------------------------------------------------------------

The personalized medicine module addresses treatment combination optimization using QAOA~\cite{farhi2014qaoa}. Given $n$ candidate treatments with efficacy scores and pairwise interaction effects, the objective is:
\begin{equation}
\max \sum_i w_i z_i + \sum_{i<j} s_{ij} z_i z_j,
\label{eq:treatment_optimization}
\end{equation}
where $z_i \in \{0,1\}$ indicates treatment inclusion, $w_i$ is individual efficacy, and $s_{ij}$ captures synergy (positive) or antagonism (negative). Prohibited combinations are enforced via QUBO penalty terms. The quantum implementation constructs an Ising Hamiltonian from the coefficients, applies QAOA with basis encoding, and returns the optimal regimen balancing efficacy with interaction constraints.

% -----------------------------------------------------------------------------
\subsection{Drug Discovery Module}
\label{subsec:drug_discovery}
% -----------------------------------------------------------------------------

The drug discovery module screens molecular compounds for biological activity using VQC~\cite{schuld2020circuit}. Molecular descriptors (weight, lipophilicity, hydrogen bond donors/acceptors, polar surface area) are angle-encoded into qubit rotations. The VQC is trained on labeled active/inactive compounds with alternating entangling CNOT gates and parameterized rotations, and classifies novel candidates with confidence probabilities from the readout qubit expectation value. The number of qubits corresponds to the number of descriptors (typically 4--8).

% -----------------------------------------------------------------------------
\subsection{Medical Imaging Module}
\label{subsec:medical_imaging_method}
% -----------------------------------------------------------------------------

The medical imaging module performs tumor detection using the neural quantum digital twin architecture~\cite{cong2019quantum}. A classical CNN extracts spatial features from medical images, reducing dimensionality to match the quantum circuit's qubit count; a quantum variational circuit then performs the final binary classification (tumor present/absent) with confidence scoring. This hybrid approach enables processing of high-dimensional images while leveraging quantum resources for the classification decision.

% -----------------------------------------------------------------------------
\subsection{Genomic Analysis Module}
\label{subsec:genomic_analysis_method}
% -----------------------------------------------------------------------------

The genomic analysis module discovers gene interaction networks from expression data using the TTN~\cite{orus2019tensor, huggins2019towards}. Gene expression profiles constitute a high-dimensional dataset where the objective is to identify significant pairwise and higher-order interactions. The hierarchical tensor structure organizes genes and learns correlation patterns at multiple scales, producing an interaction network with a hierarchical decomposition revealing the scale at which each interaction operates.

% -----------------------------------------------------------------------------
\subsection{Epidemic Modeling Module}
\label{subsec:epidemic_modeling_method}
% -----------------------------------------------------------------------------

The epidemic modeling module simulates disease spread dynamics using quantum simulation. The SIR model~\cite{kermack1927contribution} is encoded by mapping individuals to qubits ($|0\rangle$ = susceptible, $|1\rangle$ = infected), with CNOT gates modeling contact events parameterized by infection rate $\beta$ and $R_Y$ rotations modeling recovery parameterized by $\gamma$. The simulation proceeds in discrete time steps with periodic boundary conditions. The SEIR extension is supported through ancilla qubits. The output is an epidemic curve of population compartment fractions over time.

% -----------------------------------------------------------------------------
\subsection{Hospital Operations Module}
\label{subsec:hospital_operations_method}
% -----------------------------------------------------------------------------

The hospital operations module optimizes patient flow---admissions, bed allocations, and staff assignments---using QAOA~\cite{farhi2014qaoa}. The multi-objective formulation minimizes:
\begin{equation}
\min \sum_i \alpha_i f_i(\mathbf{z}) + \lambda \sum_c \text{penalty}_c(\mathbf{z}),
\label{eq:hospital_optimization}
\end{equation}
where $f_i(\mathbf{z})$ are individual objectives (wait time, utilization, staffing), $\alpha_i$ are objective weights, and penalty terms enforce capacity and availability constraints. The implementation uses $p = 2$ layers for instances with 10--20 binary decision variables, producing an optimized schedule with achieved wait time and utilization metrics.

% =============================================================================
\section{Classical Baseline Implementations}
\label{sec:classical_baselines}
% =============================================================================

Each classical baseline uses the same input data, problem formulation, and evaluation metrics as its quantum counterpart, ensuring that any performance differences are attributable solely to the computational approach. Table~\ref{tab:classical_baselines} summarizes the mappings.

\begin{table}[htbp]
\centering
\caption{Mapping of quantum algorithms to classical baseline implementations.}
\label{tab:classical_baselines}
\begin{tabular}{l l l}
\hline
\textbf{Healthcare Module} & \textbf{Quantum Algorithm} & \textbf{Classical Baseline} \\
\hline
Personalized Medicine & QAOA & Genetic Algorithm~\cite{holland1975adaptation} \\
Drug Discovery & VQC & Random Forest + Mol.\ Dynamics \\
Medical Imaging & Neural Quantum DT & CNN + SVM~\cite{cortes1995support} \\
Genomic Analysis & Tree Tensor Network & Pearson/Spearman Correlation \\
Epidemic Modeling & Quantum Simulation & Agent-based SIR/SEIR~\cite{kermack1927contribution} \\
Hospital Operations & QAOA & Linear/Integer Programming \\
\hline
\end{tabular}
\end{table}

All baselines use NumPy, SciPy, and scikit-learn in single-threaded mode for fair comparison: genetic algorithm (population 100)~\cite{holland1975adaptation}, random forest (100 estimators), RBF-kernel SVM~\cite{cortes1995support}, Pearson/Spearman correlation, agent-based SIR~\cite{kermack1927contribution}, and simplex/branch-and-bound. These represent strong classical approaches rather than trivial strawmen~\cite{preskill2018quantum}.

% =============================================================================
\section{Benchmark Methodology}
\label{sec:benchmark_methodology}
% =============================================================================

% -----------------------------------------------------------------------------
\subsection{Experimental Setup}
\label{subsec:experimental_setup}
% -----------------------------------------------------------------------------

All quantum computations are executed on the Qiskit Aer simulator~\cite{aleksandrowicz2019qiskit} using \texttt{statevector\_simulator} for exact computation and \texttt{qasm\_simulator} for shot-based sampling (1024 shots default). Ideal noise-free simulation isolates algorithmic advantage from hardware noise effects~\cite{preskill2018quantum}. The benchmark API endpoint orchestrates paired quantum and classical execution with identical input data. Figure~\ref{fig:benchmark-methodology} illustrates the methodology.

\begin{figure}[htbp]
\centering
\resizebox{\textwidth}{!}{%
\begin{tikzpicture}[
  box/.style={draw, rounded corners=3pt, minimum width=3.2cm, minimum height=0.9cm, font=\sffamily\footnotesize, align=center, thick},
  smallbox/.style={draw, rounded corners=2pt, minimum width=3cm, minimum height=1.2cm, font=\sffamily\scriptsize, align=left, thick},
  arrw/.style={-{Stealth[length=2.5mm]}, thick, qtwindark},
]
% --- Input ---
\node[box, fill=qtwindark!10] (input) at (0, 0) {Input Data};
% --- Two paths ---
\node[box, fill=classicalgray!20] (classical) at (-3.5, -1.8) {Classical Baseline};
\node[box, fill=qtwinblue!20] (quantum) at (3.5, -1.8) {Quantum Module};
% --- Results ---
\node[smallbox, fill=classicalgray!10] (cresult) at (-3.5, -3.8) {Classical Result\\[2pt]\textsf{Time, Accuracy, Scale}};
\node[smallbox, fill=qtwinblue!10] (qresult) at (3.5, -3.8) {Quantum Result\\[2pt]\textsf{Time, Accuracy, Scale}};
% --- Comparison ---
\node[box, fill=qtwinpurple!15, minimum width=4cm] (compare) at (0, -5.8) {Statistical Comparison};
% --- Validation ---
\node[box, fill=qtwingreen!12, minimum width=5.5cm, minimum height=1.2cm] (valid) at (0, -7.8) {Validation Output\\[2pt]\textsf{$p$-value $<$ 0.05,\; Cohen's $d$,\; 95\% CI,\; $n=30$ runs}};
% --- Arrows ---
\draw[arrw] (input.south) -- ++(0,-0.3) -| (classical.north);
\draw[arrw] (input.south) -- ++(0,-0.3) -| (quantum.north);
\draw[arrw] (classical) -- (cresult);
\draw[arrw] (quantum) -- (qresult);
\draw[arrw] (cresult.south) -- ++(0,-0.4) -| (compare.north west);
\draw[arrw] (qresult.south) -- ++(0,-0.4) -| (compare.north east);
\draw[arrw] (compare) -- (valid);
\end{tikzpicture}%
}
\caption{Benchmark methodology for quantum versus classical comparison.}
\label{fig:benchmark-methodology}
\end{figure}

% -----------------------------------------------------------------------------
\subsection{Metrics}
\label{subsec:metrics}
% -----------------------------------------------------------------------------

The benchmark suite evaluates four metric categories: \textit{execution time} (wall-clock, decomposed by phase), \textit{accuracy} (task-appropriate: classification accuracy/F1/sensitivity for classifiers, approximation ratio for optimization, MSE for simulation), \textit{scalability} across problem sizes constrained by $O(2^n)$ simulation memory~\cite{nielsen2010quantum}, and \textit{resource usage} (qubit count, circuit depth, gate count).

% -----------------------------------------------------------------------------
\subsection{Statistical Validation}
\label{subsec:statistical_validation}
% -----------------------------------------------------------------------------

Each of the six healthcare benchmarks is executed 30 times with different random seeds to establish distributional statistics. Because the quantum circuits are executed on the noiseless Aer statevector simulator, run-to-run variance arises exclusively from the randomized problem instances (different patient profiles, molecular libraries, population configurations) and stochastic classical optimizer trajectories (COBYLA initial points), rather than from quantum shot noise or hardware fluctuations. This low-variance regime produces very small standard deviations ($\sigma \approx 0.01$--$0.03$), which inflates Cohen's $d$ effect sizes (Section~\ref{subsec:cohens_d_inflation}) but does not compromise the validity of the paired $t$-test $p$-values or confidence intervals, which remain interpretable as measures of reliable performance differences between the quantum and classical approaches.

Each benchmark is executed for 30 independent repetitions with different random seeds. Results are reported as mean $\pm$ standard deviation with paired $t$-tests ($p < 0.05$) and 95\% confidence intervals. Effect sizes are reported using Cohen's $d$:
\begin{equation}
d = \frac{\bar{x}_Q - \bar{x}_C}{s_p}, \quad \text{where } s_p = \sqrt{\frac{(n_Q - 1)s_Q^2 + (n_C - 1)s_C^2}{n_Q + n_C - 2}},
\label{eq:cohens_d}
\end{equation}
where $\bar{x}_Q$ and $\bar{x}_C$ are quantum and classical means and $s_p$ is pooled standard deviation. Results with $d < 0.2$ are interpreted with caution as potentially not practically meaningful; results with $d > 0.8$ indicate substantial advantage or disadvantage.

% -----------------------------------------------------------------------------
\subsection{Fairness}
\label{subsec:fairness_measures}
% -----------------------------------------------------------------------------

Fair comparison is ensured through input data equivalence, problem size equivalence, metric equivalence, and comprehensive reporting of all runs including quantum underperformance---addressing criticisms of weak baselines and selective reporting~\cite{preskill2018quantum}.

% -----------------------------------------------------------------------------
\subsection{Reproducibility}
\label{subsec:reproducibility}
% -----------------------------------------------------------------------------

All circuits are exported in OpenQASM~\cite{cross2017openqasm, cross2022openqasm3} with optimized parameters and metadata. Fixed random seeds ensure bitwise reproducibility~\cite{aleksandrowicz2019qiskit}.

\subsection{Simulator-Based Evaluation: Scope and Caveats}
\label{subsec:simulator_scope}

All quantum computations in this thesis are executed on the Qiskit Aer \texttt{statevector\_simulator}, which computes the exact quantum state evolution through classical matrix multiplication of $2^n \times 2^n$ unitary matrices~\cite{aleksandrowicz2019qiskit}. This execution model has two important implications for interpreting benchmark results. First, the ``quantum'' computation is performed entirely on classical hardware; the statevector simulator does not exploit quantum mechanical phenomena but rather emulates them through exponentially scaling classical linear algebra. Consequently, wall-clock execution times reflect the classical cost of simulating the quantum algorithm, not the execution time that would be observed on a physical quantum processor. Second, the simulation is noise-free: gate operations are applied as exact unitary transformations without the decoherence, gate errors, or measurement noise present on real NISQ devices~\cite{preskill2018quantum}. The benchmarks therefore measure \emph{algorithmic advantage}---whether the quantum circuit design produces superior solutions compared to traditional classical algorithms given equivalent problem inputs---rather than \emph{hardware quantum advantage}. Cerezo et al.\ further note that classical simulability of certain variational circuits challenges the assumption that simulator-based results transfer to genuine quantum advantage~\cite{cerezo2025simulability}. The reported improvements should be interpreted as upper bounds on hardware-achievable performance, with the magnitude of degradation on physical processors remaining an open empirical question addressable through the framework's OpenQASM export capability~\cite{cross2022openqasm3}.

% =============================================================================
\section{Evaluation Framework}
\label{sec:evaluation}
% =============================================================================

The evaluation framework operates across three dimensions. \textit{Quantitative benchmarking} compares quantum versus classical performance across six healthcare modules with statistical significance testing (Section~\ref{subsec:statistical_validation}). \textit{Qualitative evaluation} assesses usability (conversation turns, response clarity) and generalizability (twin generation without code modification). \textit{Cross-domain validation} tests universality using military logistics, sports analytics, and environmental disaster response, evaluating entity extraction accuracy, algorithm selection appropriateness, and functional twin generation---all using the identical codebase~\cite{honnibal2020spacy}.
